\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage[top=0.4in, bottom=0.4in, left=0.5in, right=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{fontawesome5}

\definecolor{darkblue}{RGB}{0, 70, 140}
\hypersetup{colorlinks=true,linkcolor=darkblue,filecolor=darkblue,urlcolor=darkblue,}

\linespread{1.0}
\setlength{\parskip}{0pt}

\titleformat{\section}{\vspace{-8pt}\scshape\raggedright\large\bfseries\color{darkblue}}{}{0em}{}[\color{black}\titlerule \vspace{3pt}]

\setlist[itemize]{itemsep=1pt, parsep=0pt, topsep=1pt, leftmargin=1.0em}

\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{\vspace{2pt}\item\begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & \small \textbf{#2} \\\textit{\small #3} & \textit{\small #4} \\\end{tabular*}\vspace{-2pt}}

\begin{document}

\begin{center}
{\Huge \textbf{Cristhian Edilson Lucinger}} \\
\vspace{3pt}
\small\faMapMarker* Timbó, SC \hspace{4pt} \$|\$ \hspace{4pt}\faPhone* +55 (47) 99221-9275 \hspace{4pt} \$|\$ \hspace{4pt}\faEnvelope* \href{mailto:lucinger.cris@gmail.com}{lucinger.cris@gmail.com} \\
\vspace{1pt}
\faLinkedin* \href{https://www.linkedin.com/in/cristhian-lucinger/}{in/cristhian-lucinger} \hspace{4pt} \$|\$ \hspace{4pt}\faGithub* \href{https://github.com/Kirby6567}{github.com/Kirby6567} \hspace{4pt} \$|\$ \hspace{4pt}\faBook* \href{https://zenodo.org/records/18444596}{Zenodo (DOI)}
\end{center}

\vspace{-6pt}

\section{Professional Summary}
\small Cybersecurity Researcher and CS Undergraduate specializing in \textbf{Offensive Security (Red Team)}, \textbf{Threat Intelligence}, and \textbf{Applied Cryptography}. Creator of \textbf{Model P3}, a novel methodology for passive RSA auditing. Possesses a strong "Purple Team" mindset, bridging theoretical mathematics with practical pentesting tools (Python/Bash) for \textbf{Vulnerability Assessment}. Currently preparing for CompTIA Security+.

\section{Featured Research}
\resumeSubheading{Project: Model P3 (Algorithmic Compression Signatures)}{Jan 2026 -- Present}{Independent Researcher \& Tool Developer}{Remote}
\begin{itemize}
\resumeItem{\textbf{Innovation:} Discovered a Universal Scaling Law (\ = 1 + O/S\$) enabling deterministic \textbf{Cryptanalysis} and classification of RSA keys (2048/4096) without metadata parsing.}
\resumeItem{\textbf{Utility:} Developed a Python toolkit for \textbf{Red Team Recon Optimization}, detecting low-entropy honeypots with 100\% accuracy, mitigating \textbf{Resource Exhaustion} risks during scanning.}
\resumeItem{\textbf{Validation:} Empirically validated with N=150 samples using ZLIB, Zstandard, and Brotli algorithms.}
\resumeItem{\textbf{Output:} Technical Report published on Zenodo (DOI: 10.5281/zenodo.18444596).}
\end{itemize}

\section{Professional Experience}
\resumeSubheading{Cybersecurity \& IT Consultant}{Mar 2024 -- Present}{Independent Projects}{Remote / Hybrid}
\begin{itemize}
\resumeItem{\textbf{Red Team Operations:} Executed full-cycle Penetration Testing targeting \textbf{OWASP Top 10} (SQLi, XSS) and \textbf{Active Directory} vulnerabilities. Used Kali Linux, Nmap, Burp Suite, and Metasploit for exploitation.}
\resumeItem{\textbf{Blue Team \& Hardening:} Implemented GRC controls aligning with \textbf{NIST CSF} and \textbf{ISO 27001}. Engineered SIEM (Wazuh) decoders and Fortinet policies to detect \textbf{Lateral Movement} and reduce false positives.}
\resumeItem{\textbf{Cloud Security:} Architected \textbf{Zero Trust} access models via IAM policies and configured WAF rules across Multi-Cloud (OCI, AWS, Azure), ensuring compliance with the \textbf{Shared Responsibility Model}.}
\resumeItem{\textbf{DFIR:} Led Digital Forensics operations using Autopsy and FTK Imager. Applied \textbf{PICERL} methodology to analyze malware artifacts and preserve the \textbf{Chain of Custody}.}
\end{itemize}

\section{Technical Skills}
\begin{itemize}
\resumeItem{\textbf{Offensive:} Pentest Lifecycle, Network Scanning (Nmap), Burp Suite, Metasploit, Privilege Escalation, Wireshark.}
\resumeItem{\textbf{Research/Dev:} Python (Security Automation), Bash, LaTeX, Cryptography, HPC Cluster Mgmt, Git, Docker.}
\resumeItem{\textbf{Defensive/Cloud:} SIEM (Wazuh), IDS/IPS (Snort), Fortinet, AWS/Azure/OCI, Linux Hardening, Threat Hunting.}
\resumeItem{\textbf{Compliance:} NIST CSF, ISO 27001, MITRE ATT\&CK, LGPD/GDPR, Risk Assessment.}
\end{itemize}

\section{Certifications}
\begin{itemize}
\resumeItem{\textbf{CompTIA Security+ (SY0-701)} -- \textit{Candidate (In Preparation - Exam Scheduled 2026)}}
\resumeItem{\textbf{Google Cybersecurity Professional Certificate} -- \textit{Google}}
\resumeItem{\textbf{Fortinet Certified Associate (FCA)} -- \textit{Fortinet}}
\resumeItem{\textbf{OCI 2025 Observability \& Foundations Professional} -- \textit{Oracle}}
\resumeItem{\textbf{Professional SOC Analyst} -- \textit{IBSEC}}
\end{itemize}

\section{Education}
\resumeSubheading{Bachelor of Computer Science}{Graduation: 2027}{Anhanguera}{Brazil}
\begin{itemize}
\resumeItem{Focus: Methods in Applied Mathematics, Network Security, Data Structures, Algorithms.}
\resumeItem{\textbf{Specializations (Bootcamps):} Offensive Cybersecurity, Defensive Security, Digital Forensics (XP Educação).}
\end{itemize}

\end{document}
